|

### 2019-09-03 appendix/appendix.Rmd
Appendix commit Mignozzetti

# Load Data 
load('tdp.RData')

# Covariate Balance -- Intervention 1
aux <- select(impEvalph1, treatOriginal, logPop2015, ideb_ai_2015, 
              ideb_af_2015, log_poorFam2010, log_totTransf2016) %>% unique()

resu1 <- compareGroups(treatOriginal ~ logPop2015 + log_poorFam2010 +
                         log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
                       data = aux)

@@

```{r}
## Covariate balance
aux <- select(impEvalph2, logPop2015, treatApp, ideb_ai_2015,
              ideb_af_2015, log_poorFam2010, log_totTransf2016)

resu1 <- compareGroups(treatApp ~ logPop2015 + log_poorFam2010 +
                         log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
                       data = aux)

@@

```{r man1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1. The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
# Map manipulation test -- Intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impEvalph2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

@@

```{r man2, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2. The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
## Map manipulation test -- Intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impEvalph2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

@@

```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
load('tdp.RData')

@@

# Auxiliary function: calculate coefficients
calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  dataux <- dat
  k <- 1
  for (i in treats) {
    for (j in outcs) {
      if(is.null(wts)) {
        dat <- dataux %>%
          select(one_of(c(j, treats, ctrls, fes, cls))) %>%
          na.omit()
        } else {
          dat <- dataux %>%
            select(one_of(c(j, treats, ctrls, fes, cls, wts))) %>%
            na.omit()
          wts <- dat[,wts]
        }
      # No controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = F))
      print(k); k = k+1
      # Controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = F))
      print(k); k = k+1
      # No controls and fes
      mods[[k]] <- felm(
        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
                                   paste('',fes_mod,0,cls, sep = '|'), 
                                   sep = '')),
                         collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = T))
      print(k); k = k+1
      # Controls and fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = T))
      print(k); k = k+1
    }
  }
  return(list(moddescr, mods))
}

@@

resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)

# Results intervention 1
stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
          resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
                             "Yes", "Yes", "Yes"),
            c("State fixed effects", "Yes", "Yes", "Yes",
              "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)
```

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & 1.26 & 1.83 & 0.57 & 0.05$^{***}$ & 0.03$^{***}$ & 0.06 \\ 
  & (2.69) & (3.06) & (0.93) & (0.01) & (0.01) & (0.04) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 3,602 & 3,602 & 3,602 & 3,602 & 3,602 & 2,352 \\ 
R$^{2}$ & 0.13 & 0.13 & 0.05 & 0.03 & 0.05 & 0.08 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

@@

```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
load('tdp.RData')

@@

resInt2 <- calcATEs(outcs, 'treatApp', ctrls, fes, cls, dat = impEvalph2)

# Results intervention 2
library(stargazer)
stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
          dep.var.labels.include=F, 
          keep='treatAppTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)
```

@@

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impEvalph1)[1]

# Excluded
excld <- sum(is.na(impEvalph1$treat))

@@

# On treatment
tralloc <- sum(impEvalph1$treat=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impEvalph1$treat=='Control', na.rm = T)

@@

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impEvalph2)[1]

# Excluded
excld <- sum(is.na(impEvalph2$treatApp))

@@

# On treatment
tralloc <- sum(impEvalph2$treatApp=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impEvalph2$treatApp=='Control', na.rm = T)

>>>>

# Load Data 
load('../article/tdp.RData')

# Covariate Balance -- Intervention 1
aux <- select(impact_evaluation_phase1, treat, logPop2015, ideb_ai_2015, 
              ideb_af_2015, log_poorFam2010, log_totTransf2016) %>% unique()

resu1 <- compareGroups(treat ~ logPop2015 + log_poorFam2010 +
                         log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
                       data = aux)

@@

```{r}
## Covariate balance
aux <- select(impact_evaluation_phase2, treat, logPop2015, ideb_ai_2015,
              ideb_af_2015, log_poorFam2010, log_totTransf2016)

resu1 <- compareGroups(treat ~ logPop2015 + log_poorFam2010 +
                         log_totTransf2016 + ideb_ai_2015 + ideb_af_2015,
                       data = aux)

@@

```{r man1, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation1}Manipulation checks for intervention 1. The first plot shows the geographical distribution of the treatment condition and the second graph displays the number of TDP app downloads from August 2017 to February 2018.'}
# Map manipulation test -- Intervention 1
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase1 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
pMapDownloadsInt1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
pMapDownloadsInt1

@@

```{r man2, echo=TRUE, warning=FALSE, message=FALSE, error=FALSE, cache=TRUE, out.width='.49\\linewidth', fig.width=4, fig.height=4, fig.show='hold', fig.align='center', fig.cap='\\label{fig:manipulation2}Manipulation checks for intervention 2. The graphs display the geographical and temporal variation of TDP app downloads from August 2018 to February 2019.'}
## Map manipulation test -- Intervention 2
mapbr <- get_brmap('City')
gaaux <- filter(ga, phase2 == 1)
gaaux <- select(gaaux, ibge_code7, downl)
gaaux <- rename(gaaux, City = ibge_code7)
gaaux <- unique(gaaux)
gaaux$City <- as.numeric(gaaux$City)
gaaux2 <- impact_evaluation_phase2 %>%
  select(ibge_code7) %>%
  transmute(City = as.numeric(ibge_code7)) %>%
  unique()
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 0
gaaux2 <- data.frame(City = mapbr$City)
gaaux <- merge(gaaux2, gaaux, all.x = TRUE); rm(gaaux2)
gaaux$downl[is.na(gaaux$downl)] = 2
gaaux$Downloads <- factor(gaaux$downl, labels = c('No Downloads', 'Downloads',
                                                  'Not in App'))
mapbr <- join_data(mapbr, gaaux, by = 'City')
p1 <- ggplot() + 
  geom_sf(data = mapbr, aes(fill = Downloads), lwd = 0.02) +
  scale_fill_manual(values=c( "#E69F00", "#0072B2", "#F0E442")) +
  theme_map()
p1

@@

```{r int1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
load('../article/tdp.RData')

@@

# Auxiliary function: calculate coefficients
calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  dataux <- dat
  k <- 1
  for (i in treats) {
    for (j in outcs) {
      if(is.null(wts)) {
        dat <- dataux %>%
          select(one_of(c(j, treats, ctrls, fes, cls))) %>%
          na.omit()
        wtsaux <- NULL
      } else {
          dat <- dataux %>%
            select(one_of(c(j, treats, ctrls, fes, cls, wts))) %>%
            na.omit()
          wtsaux <- dat[,wts]
      }
      # No controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = F))
      print(k); k = k+1
      # Controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = F))
      print(k); k = k+1
      # No controls and fes
      mods[[k]] <- felm(
        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
                                   paste('',fes_mod,0,cls, sep = '|'), 
                                   sep = '')),
                         collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = T))
      print(k); k = k+1
      # Controls and fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wtsaux)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = T))
      print(k); k = k+1
    }
  }
  return(list(moddescr, mods))
}

@@

resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impact_evaluation_phase1)

# Results intervention 1
stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
          resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
                             "Yes", "Yes", "Yes"),
            c("State fixed effects", "Yes", "Yes", "Yes",
              "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)

# Results intervention 1 -- No Controls and No Fixed Effects
stargazer(resInt1[[2]][[1]],resInt1[[2]][[5]],resInt1[[2]][[9]],
          resInt1[[2]][[13]],resInt1[[2]][[17]],resInt1[[2]][[21]],
          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1 \\\\ No Controls and No Fixed Effects', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "No", "No", "No", 
                             "No", "No", "No"),
            c("State fixed effects", "No", "No", "No",
              "No", "No", "No")),
          notes.append = T, header=FALSE)

# Results intervention 1 -- No Controls
stargazer(resInt1[[2]][[3]],resInt1[[2]][[7]],resInt1[[2]][[11]],
          resInt1[[2]][[15]],resInt1[[2]][[19]],resInt1[[2]][[23]],
          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1 \\\\ No Controls', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "No", "No", "No", 
                             "No", "No", "No"),
            c("State fixed effects", "Yes", "Yes", "Yes",
              "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)

# Results intervention 1 -- No Fixed Effects
stargazer(resInt1[[2]][[2]],resInt1[[2]][[6]],resInt1[[2]][[10]],
          resInt1[[2]][[14]],resInt1[[2]][[18]],resInt1[[2]][[22]],
          title = '\\label{tab:results1} Impact Evaluation -- Intervention 1 \\\\ No Fixed Effects', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipality level.',
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
                             "Yes", "Yes", "Yes"),
            c("State fixed effects", "No", "No", "No",
              "No", "No", "No")),
          notes.append = T, header=FALSE)

```

@@

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & $-$0.99 & $-$1.12 & $-$0.13 & 0.002 & 0.02$^{**}$ & 0.05 \\ 
  & (2.59) & (2.96) & (1.03) & (0.01) & (0.01) & (0.05) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
R$^{2}$ & 0.16 & 0.14 & 0.05 & 0.02 & 0.07 & 0.13 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

The models without control variables or fixed effects follow below.

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1 \\ No Controls and No Fixed Effects} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & $-$0.21 & $-$0.56 & $-$0.36 & 0.01 & 0.02$^{**}$ & 0.04 \\ 
  & (4.10) & (4.86) & (1.21) & (0.01) & (0.01) & (0.07) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & No & No & No & No & No & No \\ 
State fixed effects & No & No & No & No & No & No \\ 
Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
R$^{2}$ & 0.0000 & 0.0000 & 0.0001 & 0.0001 & 0.001 & 0.001 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1 \\ No Controls} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & $-$2.20 & $-$2.08 & 0.12 & 0.003 & 0.03$^{**}$ & 0.03 \\ 
  & (2.87) & (3.33) & (1.06) & (0.01) & (0.01) & (0.05) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & No & No & No & No & No & No \\ 
State fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
R$^{2}$ & 0.07 & 0.06 & 0.04 & 0.01 & 0.05 & 0.06 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:results1} Impact Evaluation -- Intervention 1 \\ No Fixed Effects} 
  \label{} 
\begin{tabular}{@{\extracolsep{-2pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
 & Investment & Investment & Delta & Finished & Cancelled & Updated \\ & Before & After & Investment & Construction & Construction & Date \\ &  &  &  &  &  \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 ATE & 1.23 & 0.82 & $-$0.41 & 0.01 & 0.02$^{**}$ & 0.06 \\ 
  & (3.59) & (4.14) & (1.06) & (0.01) & (0.01) & (0.06) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Controls & Yes & Yes & Yes & Yes & Yes & Yes \\ 
State fixed effects & No & No & No & No & No & No \\ 
Observations & 2,986 & 2,986 & 2,986 & 2,986 & 2,986 & 2,926 \\ 
R$^{2}$ & 0.11 & 0.10 & 0.02 & 0.01 & 0.02 & 0.08 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{6}{r}{Cluster-robust SEs at the municipality level.} \\ 
\end{tabular} 
\end{table}

@@

```{r int2, echo=FALSE, warning=FALSE, message=FALSE, results='hide',cache=TRUE}
load('../article/tdp.RData')

@@

resInt2 <- calcATEs(outcs, 'treat', ctrls, fes, cls, dat = impact_evaluation_phase2, wts = 'IPW_treat')

# Results intervention 2
library(stargazer)
stargazer(resInt2[[2]][[4]],resInt2[[2]][[8]],resInt2[[2]][[12]],
          resInt2[[2]][[16]],resInt2[[2]][[20]],resInt2[[2]][[24]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2',
          dep.var.labels.include=F, 
          keep='treatAppTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes"),
            c("State Fixed Effects", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)

# Results intervention 2 -- No Controls and No Fixed Effects
stargazer(resInt2[[2]][[1]],resInt2[[2]][[5]],resInt2[[2]][[9]],
          resInt2[[2]][[13]],resInt2[[2]][[17]],resInt2[[2]][[21]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2 \\\\ No Controls and No Fixed Effects', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
          add.lines = list(c("Controls", "No", "No", "No", 
                             "No", "No", "No"),
            c("State fixed effects", "No", "No", "No",
              "No", "No", "No")),
          notes.append = T, header=FALSE)

# Results intervention 1 -- No Controls
stargazer(resInt2[[2]][[3]],resInt2[[2]][[7]],resInt2[[2]][[11]],
          resInt2[[2]][[15]],resInt2[[2]][[19]],resInt2[[2]][[23]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2 \\\\ No Controls', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
          add.lines = list(c("Controls", "No", "No", "No", 
                             "No", "No", "No"),
            c("State fixed effects", "Yes", "Yes", "Yes",
              "Yes", "Yes", "Yes")),
          notes.append = T, header=FALSE)

# Results intervention 1 -- No Fixed Effects
stargazer(resInt2[[2]][[2]],resInt2[[2]][[6]],resInt2[[2]][[10]],
          resInt2[[2]][[14]],resInt2[[2]][[18]],resInt2[[2]][[22]],
          title = '\\label{tab:results2} Impact Evaluation -- Intervention 2 \\\\ No Fixed Effects', 
          keep='treatTreatment', 
          type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c("Investment & Investment & Delta & Finished & Cancelled & Updated \\\\ & Before & After & Investment & Construction & Construction & Date \\\\"),
          dep.var.labels.include=F, column.sep.width = '-2pt',
          omit.stat=c('adj.rsq', 'ser'), align=F, digits=2,
          notes = c('Cluster-robust SEs at the municipality level.', 'IPW computed using the randomizr package'),
          add.lines = list(c("Controls", "Yes", "Yes", "Yes", 
                             "Yes", "Yes", "Yes"),
            c("State fixed effects", "No", "No", "No",
              "No", "No", "No")),
          notes.append = T, header=FALSE)
```

@@

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impact_evaluation_phase1)[1]

# Excluded
excld <- sum(is.na(impact_evaluation_phase1$treat))

@@

# On treatment
tralloc <- sum(impact_evaluation_phase1$treat=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impact_evaluation_phase1$treat=='Control', na.rm = T)

@@

```{r, echo=FALSE}
# Values ------------------------------------------------------------------
# Total dataset
ntotini <- dim(impact_evaluation_phase2)[1]

# Excluded
excld <- sum(is.na(impact_evaluation_phase2$treat))

@@

# On treatment
tralloc <- sum(impact_evaluation_phase2$treat=='Treatment', na.rm = T)

# Control
ctrlalloc <- sum(impact_evaluation_phase2$treat=='Control', na.rm = T)
